### 2020-05-25 README.Rmd
fst grep TODOs
grep include scripts/
add manuscript todos to README
rm badges
update README

<!-- badges: start -->
<!-- badges: end -->

@@

## Info
[Special Column info](https://academic.oup.com/CZ/pages/animal_social_system)

### Deadlines
* ~~Abstract submission: 30 August 2019~~
* Manuscript submission: 31 January 2020
* Printing: June 2020

### Guidelines
[General Instructions page](https://academic.oup.com/cz/pages/General_Instructions)

>>>>

@@

## TODO
```{bash}
grep -rni 'R/' -e 'TODO' || true;
grep -rni 'scripts/' -e 'TODO' || true;
grep -rni 'paper/manuscript.Rmd' -e 'TODO' || true;
```
